---
title: "Poisson Distribution"
output: html_notebook
---

Its just like Jupiter Notebook. But for math and stuff.

Poisson Distribution. When N continues to grow very very large (number of Asteroids in the solar system) while p becomes very very small (?robability of said asteroid hitting Earth) or in assignment 2 number of hours in a day and probability of consuing coffee within a given time.

Probability Mass Function of a Poisson Distribution

Prob(X = n) = (e^-??)((??^n)/n!) n = 0,1,2,3,4...

This is limiting process of Poisson Distributin

```{r}

n <- 10^(1:3)
x <- 0:10

plot(x,x*0.03, main = "Poisson Distribution as a result of Limiting Process of the Binomial Distribution\n",type='n')
cols <- c("red","orange", "yel?ow", "green", "blue", "purple")
for(i in seq_along(n)){ 
  points(x,dbinom(x,n[i],4/n[i]),pch=16,col=cols[i]) 
  } 

points(x,dpois(x,4),type='l') 
legend("topright", 
       legend=c("n=10, p=0.4","n=100, p=0.04", "n=1000, p=0.004","Poisson"), 
       pch?c(16,16,16,NA),
       col=c(cols[seq_along(n)],"red"),lty=c(NA,NA,NA,1))


```

```{r}
#clear plot

numVector <- 0:30
lambdaParam <- 6

plot(numVector, dpois( numVector, lambdaParam ), main = "Plot Distribution\n", xlim=c(-2,30))
normden <- function(x){dn?rm(x, mean=lambdaParam, sd=sqrt(lambdaParam))}
curve(normden, from=-4, to=30.5, add=TRUE, col="red")

abline(v=qpois(0.95,6))


```

Suppose that lambda = 3.1 and we observe X = 7
where X is given a Poisson distribution

p value is defined as the probabili?y that Given that the Null is true of finding a similar observation (X =7) or an observation more extreme (x >7). 

What is the precise value of p-value for observation = 7
```{r}



cat(paste("In-formal definiton of P value is the Probability that given t?e Null is true (Ho: ?? = 3.1) of seeing Obs or an Obs more extreme i.e. whether            Obs X = 7 is sufficient evidence that ?? > 3 (H1).\n", 
           "The Precise Definition of P value: P( X ??? 7| ?? = 3) ", sep =" \n"))


```

Calculate the P value for this obs X = 7 and Interpret

```{r}
print("Given a Significance of 5%")
qpois(0.95, 3.1)
ppois(6,3.1)

```
```{r}

```

Add a new chunk by by pressing *Ctrl+Alt+I*.

Calculate the P value for this obs?X = 7 and Interpret

```{r}

lambda <- seq(from=1,to=10,len=100) 
plot(lambda,dpois(7,lambda),main='Likelihood function for lambda')
 

```

