---
title: "SLeep Coffee Productivity Portfolio"
output: html_notebook
---

Its like Juppiter Notebook but for science

Run Chunk *Ctrl+Shift+Enter*
Add Chunck *Ctrl+Alt+I*
HTML Preview *Ctrl+Shift+K*

```{r}

print("Portfolio Assignment")


```

```{r}

myData <- read.csv('./data/sleepCoffeeProductivity.csv')

cat("Is data a dataframe: ", is.data.frame(myData), "\n")
cat("Dataset Contains: ", ncol(myData), " Attributes\n")
cat("Dataset Contains: ", nrow(myData), " Instances")


```

```{r}
print("Preliminary Eyeball Data: ")
cat("Max Morning Productivity: ", max(myData$Day.Productivity), "\n")
cat("Mean Morning Productivity: ", mean(myData$Day.Productivity), "\n\n")

cat("Max Night Productivity: ", max(myData$Night.Time.Productivity), "\n")
cat("Mean Night Productivity: ", mean(myData$Night.Time.Productivity))


```

First Test, Am I a morning person or a night person. T Test. We want to Aswer the question of whether I am Morning person or night person. Is more work done when sun is up or sun is down?

We use students t test on two samples of day time productivity and night time


```{r}

t.test(myData$Day.Productivity, myData$Night.Time.Productivity, paired=TRUE)


```

Addicted to Coffe or not


```{r}

addictP <- sum(dhyper(4:10, 10,25,9))

cat("Our P value to test for addiction is: ", addictP, " Our p value is: ", addictP*100, "%")

```
The probability if we do not have an addiction, of seeing the observation (X = 4) or an observation more extreme. The p value is not significant from we obs. We fail to reject the null

I do not have an addiction to caffene.

```{r}


#Verify
x <- 0:10
plot(x, dhyper(x,10,25,9),type='h',lwd=4,col=c(rep("black",5),rep("red",3)))
legend("topright",lwd=4, col=c("black","red"),legend=c("regular points","more extreme"))


```
```{r}

addictMatrix <- matrix(c(4,6,5,20),2,2,byrow=TRUE)
dimnames(addictMatrix) <- list (week=c("End","Day"),  drinkingHabit=c("Abuse","Normal") )
addictMatrix

fisher.test(addictMatrix, alternative="greater")

```

Poisson distribution test whether more cups of coffe is = productivity. We need to find Lambda.

```{r}

lambda <- mean(myData$Total.Daily.Productivity)


```

Test test

```{r}

lambdaSeq <- seq(from = 0, to = 5 , len = 100)
plot(lambdaSeq, dpois(3,lambdaSeq), main = "likelihood for lambda")
abline(v = lambda )

```

```{r}

suppCurve <- dpois(3, lambdaSeq, log = TRUE)
plot(lambdaSeq,suppCurve-max(suppCurve),main='support function for lambda')
abline(v=lambda)


```

We can infer that lambda = 2.83 is bang on the money. It is acceptable to be used in our model.

```{r}

critcalObs <- qpois(0.95, lambda ) 
pVal <- ppois(critcalObs,lambda ) 


plot(0:20, dpois( x=0:20, lambda=2.83 ), xlim=c(-2,20))
normden <- function(x){dnorm(x, mean=2.83, sd=sqrt(2.83))}
curve(normden, from=-4, to=20, add=TRUE, col="purple")

abline(v=critcalObs, col = "red" ) 
abline(v=3, col = "blue")


```

conclusion is that we fail to reject the Null

```{r}
typeof(myData$Sleep.Time)

cat("\n")

myData$Sleep.Time

#max(myData$Sleep.Time)
cat("\n")

sleepTImeCol <- format(as.POSIXct(myData$Sleep.Time,format="%l:%M:%S"),"%H%M%S")
sleepTImeCol

cat("\n")

head(sleepTImeCol)
cat("\n\n\n\n")
tail(sleepTImeCol)

cat("\n")

max(sleepTImeCol)
min(sleepTImeCol)

cat("\n")
# <- as.Date(myData$Sleep.Time)
#test <- as.POSIXlt(as.Date(myData$Sleep.Time))

```


"Drinking coffee at after 8 leads to a sleepless night"



